On the Functionality of the Multilayer Perceptron

### 2020-11-28 Thesis/Drafts/Buell-PHYS799-ThesisDraft0.tex
Minor updates to thesis draft

\paragraph*{}The ability to classify time-series data into unique categories has become topic of much attention in the last few decades \cite{Khan}. These signals can take the form of day-to-day topics such as weather measurements, financial reports, or audio-visual media, and extend into disciplines of medicine, physics, and digital signal processing. In all cases, we explore a problem where the task to categorize the sample, or subset of the sample into one of $k$ \textit{bins} called classes \cite{Mierswa,Virtanen,Geron}.

\paragraph*{}For this classification task, we have developed an automated model (called a \textit{classifier}) which can process information from a time-series audio file, and group the file based on it's prediction of what produced the sound in that file. For example, classifying an audio file which contains the waveform of a clarinet sustaining a single note should return the classification prediction of "clarinet" and so forth. This non-trivial task requires developing a model

 Developments in computational efficiency and the age of \textit{Big Data} has lead to a staggering increase in the utilization

@@

\paragraph*{}To ensure that these data sets are formatted consistently, we read each sample from it's original format, \textit{.AIF}, \textit{.MP3}, or similar, and rewrite the data as a new \textit{.WAV} files, sampled at 44.1 kHz with a 16 bit depth. This ensures that all data will have a consistent format when features are extracted. This stage is detailed in sec.(\ref{subsubsec-Preprocessing}).
% ================================================================

@@

\paragraph*{}Step (ii.) is usually given by some \textit{activation function}:
\begin{equation}
\label{eqn-elementActivation}
x^{(l)} = \sigma^{(l)} \big[ z^{(l)} \big]
\end{equation}
Where $x^{(l)}$ is the final activations for layer $l$ and $z^{(l)}$ is given in equation (\ref{eqn-LinearTransform}). $\sigma^{(l)}$ is some activation function which introduces the ability to account for non-linearity in the

\paragraph*{}The combination of Eq. (\ref{eqn-LinearTransform}) and Eq. (\ref{eqn-elementActivation}), for a layer $l$ , make up the function represented by that layer, as in Eq. (\ref{eqn-altLayerFunction}). Below, we discuss and describe the types of layer functions that are used to produce the classification model in this project.

@@

\paragraph*{}The Linear Dense Layer, often just called a \textit{Dense} Layer, or \textit{Fully-Connected} layer, was one of the earliest function types used in artificial neural network models \cite{Geron2,Loy,McCulloch}. They are among the most commonly used layer types. A dense layer is composed of a layer of \textit{artificial neurons}, each of which holds a numerical value within it, (usual a double-precision floating point number) called the \textit{activation} of that neuron. This idea was developed from McCulloch and Pitts' work \cite{McCulloch} in attempting to model cognitive processes as mathematical functions, and was expanded upon by Frank Rosenblatt in  1957 by combining many dense layers together to form a multilayer perceptron (MLP) \cite{Geron,Loy,Levine}.

@@

Thus for a dense layer $l$, the exact values of each activation is given by \cite{Geron,Loy}:
\begin{equation}
\begin{bmatrix}
x_0 \\ x_1 \\ \vdots \\ x_{n-1}
\end{bmatrix}^{(l)} =
\sigma^{(l)} \Bigg(
\begin{bmatrix}
w_{0,0} & w_{0,1} & \hdots & w_{0,m-1} \\
w_{1,0} & w_{1,1} & \hdots & w_{1,m-1} \\
\vdots & \vdots & \ddots & \vdots  \\
w_{n-1,0} & w_{n-1,1} & \hdots & w_{n-1,m-1} 
\end{bmatrix}^{(l)} 
\begin{bmatrix}
x_0 \\ x_1 \\ \vdots \\ x_{m-1}
\end{bmatrix}^{(l-1)} +
\begin{bmatrix}
b_0 \\ b_1 \\ \vdots \\ b_{n-1}
\end{bmatrix}^{(l)} \Bigg)
\end{equation}
or more compactly:
\begin{equation}
\label{eqn-DenseFeedForward}
x^{(l)} = \sigma^{(l)} \Big( W^{(l)} x^{(l-1)} + b^{(l)} \Big)
\end{equation}
Eq. (\ref{eqn-DenseFeedForward}) is generally referred to as the \textit{dense layer feed-forward equation} \cite{Goodfellow}. \textcolor{red}{How Do I finish this section? Uses of Dens layer, physical meaning?}

>>>>

\paragraph*{}The ability to classify time-series data into unique categories has become topic of much attention in the last few decades \cite{Khan}. These signals can take the form of day-to-day topics such as weather measurements, financial reports, or audio-visual media, and extend into more niche disciplines of medicine, physics, and digital signal processing.

\paragraph*{}Recent progress in high performance computing and computational efficiency have given rise to another burst

@@

\paragraph*{}To ensure that these data sets are formatted consistently, we read each sample from it's original format, \textit{.AIF}, \textit{.MP3}, or similar, and rewrite the data as a new \textit{.WAV} files, sampled at 44.1 kHz with a 16 bit depth. This ensures that all data will have a consistent format when features are extracted. This stage is detailed in sec.(\ref{subsubsec-Preprocessing}).

@@

\paragraph*{}Step (ii.) is usually given by some \textit{activation function}:
\begin{equation}
\label{eqn-elementActivation}
x^{(l)} = \sigma^{(l)} \big[ z^{(l)} \big]
\end{equation}
Where $x^{(l)}$ is the final activations for layer $l$ and $z^{(l)}$ is given in equation (\ref{eqn-LinearTransform}). $\sigma^{(l)}$ is some activation function which introduces the ability to account for non-linearity in the decision boundaries. The combination of Eq. (\ref{eqn-LinearTransform}) and Eq. (\ref{eqn-elementActivation}), for a layer $l$ , make up the function represented by that layer, as in Eq. (\ref{eqn-altLayerFunction}). In this, we discuss and describe the types of layer functions that are used to produce the classification model in this project.

@@

\paragraph*{}The Linear Dense Layer, often just called a \textit{Dense} Layer, or \textit{Fully-Connected} layer, was one of the earliest and most common function types used in artificial neural network models \cite{Geron2,Loy,McCulloch}. A dense layer is composed of a layer of \textit{artificial neurons}, each of which holds a numerical value within it, (usually a double-precision floating point number) called the \textit{activation} of that neuron. This idea was developed from McCulloch and Pitts' work \cite{McCulloch} in attempting to model cognitive processes as mathematical functions, and was expanded upon by Frank Rosenblatt in  1957 by combining many dense layers together to form a multilayer perceptron (MLP) \cite{Geron,Loy,Levine}.

@@

Thus for a dense layer $l$, the exact values of each activation is given by \cite{Geron,Loy}:
\begin{equation}
\begin{bmatrix}
x_0 \\ x_1 \\ \vdots \\ x_{n-1}
\end{bmatrix}^{(l)} =
\sigma^{(l)} \Bigg(
\begin{bmatrix}
w_{0,0} & w_{0,1} & \hdots & w_{0,m-1} \\
w_{1,0} & w_{1,1} & \hdots & w_{1,m-1} \\
\vdots & \vdots & \ddots & \vdots  \\
w_{n-1,0} & w_{n-1,1} & \hdots & w_{n-1,m-1} 
\end{bmatrix}^{(l)} 
\begin{bmatrix}
x_0 \\ x_1 \\ \vdots \\ x_{m-1}
\end{bmatrix}^{(l-1)} +
\begin{bmatrix}
b_0 \\ b_1 \\ \vdots \\ b_{n-1}
\end{bmatrix}^{(l)} \Bigg)
\end{equation}
or more compactly:
\begin{equation}
\label{eqn-DenseFeedForward}
x^{(l)} = \sigma^{(l)} \Big( W^{(l)} x^{(l-1)} + b^{(l)} \Big)
\end{equation}
Eq. (\ref{eqn-DenseFeedForward}) is generally referred to as the \textit{dense layer feed-forward equation} \cite{Goodfellow}.

\paragraph*{}The dense layer acts as an
